Corpus Stats

### 2019-03-26 notebooks/corpus_stats_and_plots.Rmd

```{r}
library(reshape2)
library(ggplot2)

@@

@@

r_counts <- r_counts[pkgs_to_plot]
c_counts <- c_counts[pkgs_to_plot]
records_by_fun[ "pkg" ] <- rownames(records_by_fun) # needed for plotting

records_by_fun <- records_by_fun[records_by_fun[,"pkg"] %in% pkgs_to_plot, ]

@@

plot_both <- plot_both + theme(
  axis.text.x  = element_blank(), 
  axis.title.x = element_blank(),
  axis.ticks.x = element_blank(),
  axis.ticks.y = element_line(), 
  panel.grid.major.y = element_line(colour = "red")) + # ,
  # panel.ontop = T) + 
  scale_y_continuous(name="Lines of Code in Package", breaks = c(-4, -3, -2, -1, 0, 1, 2, 3, 4), 
                     labels = c(10000, 1000, 100, 10, 0, 10, 100, 1000, 10000)) # +
  # scale_x_discrete(name="Package", breaks = unlist(loc_of_top_10[!(loc_of_top_10 == FALSE)]), labels = top_10)
  # geom_line(aes( x, y), cut_top) +
  # geom_line(aes( x, y), cut_bot)

@@

records_by_fun$pkg <- factor(records_by_fun$pkg, levels=combo_df$package_name)
# log scale?
records_by_fun$invo_obs <- sapply(records_by_fun$invo_obs, function(x) if (x == 0) x else log10(x))

plot_records <- ggplot(data=records_by_fun, aes(x=pkg, y=invo_obs, group=1)) +
                geom_line(size=0.25) + 
                labs( title = "Numbers of Observed Signatures",
                      y = "Observed Invocations in Pkg (Thousands, log10-Scaled)") +
                theme(axis.text.x = element_blank(), axis.title.x=element_blank(),
                      axis.ticks.x=element_blank()) +
                scale_y_continuous(breaks = c(0, 1, 2, 3, 4, 5, 6), 
                     labels = c(0, 10, 100, 1000, 10000, 100000, 1000000))

>>>>

```{r}
library(reshape2)
library(ggplot2)
library(ggrepel)

@@

total_recorded_sigs <- readRDS("../data/final_recorded_sigs_by_package.RDS")

@@

r_counts <- r_counts[pkgs_to_plot]
c_counts <- c_counts[pkgs_to_plot]
total_recorded_sigs <- total_recorded_sigs[pkgs_to_plot]

records_by_fun[ "pkg" ] <- rownames(records_by_fun) # needed for plotting
records_by_fun <- records_by_fun[records_by_fun[,"pkg"] %in% pkgs_to_plot, ]
records_by_fun$invo_rec <- unlist(total_recorded_sigs)

@@

plot_both <- plot_both + theme(
  axis.text.x  = element_blank(), 
  axis.title.x = element_blank(),
  axis.ticks.x = element_blank(),
  axis.ticks.y = element_line(), 
  panel.grid.major.y = element_line(colour = "red")) + # ,
  # panel.ontop = T) + 
  scale_y_continuous(name="Lines of Code in Package", breaks = c(-4, -3, -2, -1, 0, 1, 2, 3, 4), 
                     labels = c(10000, 1000, 100, 10, 0, 10, 100, 1000, 10000)) +
  geom_text_repel(data=subset(zzz, package_name %in% top_10 & language == "loc_r"),
                  aes(y = 0, label=package_name), position=position_dodge(0.9), direction="y")
  # trying to get some text to show up

@@

records_by_fun$pkg <- factor(records_by_fun$pkg, levels=combo_df$package_name)
# log scale?
# records_by_fun$invo_obs <- sapply(records_by_fun$invo_obs, function(x) if (x == 0) x else log10(x))

plot_records <- ggplot(data=records_by_fun, aes(x=invo_obs, y=invo_rec)) +
                geom_point(size=0.25) + 
                labs( title = "Numbers of Observed Signatures",
                      y = "Recorded Invocations in Pkg (Thousands)",
                      x = "Observed Invocations in Pkg (Thousands)") +
                theme(axis.text.x = element_blank(), axis.title.x=element_blank(),
                      axis.ticks.x=element_blank()) #+
                # scale_y_continuous(breaks = c(0, 1, 2, 3, 4, 5, 6),
                #      labels = c(0, 10, 100, 1000, 10000, 100000, 1000000))
